\mytitle

### 2020-04-20 paper.tex
Modify the order of columns on both tables.
eval.

In this section, we 
present an empirical evaluation of the two quadratic models based on 
standard WFLO instances.
Our main results are: \begin{itemize}
	\item QUBO based WFLO using the digital annealer is competitive with exact methods. 
	\item Given sufficient runtime the QCOP model provides superior results compared to state-of-the-art methods.
	\item The runtime for solving the QUBO model is two orders of magnitude lower than QCOP. 
\end{itemize}
We start by outlining the experimental design of our evaluation, followed by a presentation of our main results
and a discussion of the results together with the limitations of the approach.

@@

\paragraph{WFLO Setting and Measurements}

To test and benchmark our models, we used 12 standard benchmark WFLO instances
from the literature~\cite{MOSETTI1994105,Zhang2014,grady2005placement}. 
The 12 benchmarks result from varying 2 wind settings (1 and 36 wind directions),
2 grid sizes ($10\times10$ with cell size $200$ meters and $20\times20$ with cell size $100$ meters),
and 3 variations for number of turbines ($m \in \{20, 30 or 40\}$).
The wind regime distribution presented in Figure~\ref{fig:prob_wind} was 
elicited from~\cite{Zhang2014}.
Additional parameters that were used to calculate 
the velocities ($u_{id\infty}, u_{ijd}$) include: turbine height ($60$ meters),
ground roughness ($0.3$ meters), turbine rotor radius ($20$ meters), and a wind farm of size $2km \times 2km$.
We have measured solutions using the SS energy expression.
To to this end, we converted solutions that came from LS based methods into the corresponding SS expression.
Lastly, the total mean energy is presented in $kW/year$.

@@

We compared our two models, namely QCOP and QUBO, against two state of the art exact optimization methods:
the integer linear programming (ILP-LS) approach from~\cite{donovan2005wind}, and the 
model that uses a quadratic approximation (QP-SS)~\cite{turner2014new}. The CP approach presented in~\cite{Zhang2014} was
reported to perform worse than the rest and was left out of the experiments.
We used state of the art software, namely Gurobi~\cite{gurobi}, to solve QCOP, ILP-SS and QP-SS, and 
applied both Fujitsu's digital annealer and GUrobi to solve QUBO.

@@

\todo{Explain how we solved WFLO using the various instances}

\paragraph{Implementation Details}

@@

	\begin{tabular}{| c | c | c | c | c | c | c | c |}
		\toprule
		Wind Directions  & n        & m        & ILP-LS       & QP-LS       & QUBO-LS       & QP-SS       & DA-LS     \\
		\toprule
		\multirow{6}{*}{WR1}  & \multirow{3}{*}{10}       & 20       & \textbf{11185.41} & \textbf{11185.41} & \textbf{11185.41} & \textbf{11185.41} & \textbf{11185.41} \\
		& & 30   & 15739.57 & 15738.45 & \textbf{15742.93} & 15735.1  & 15740.69         \\
		& & 40 & \textbf{19265.21} & \textbf{19265.21} & 18952.97 & \textbf{19265.21} & \textbf{19265.21}                \\
		\cline{2-8}
		&\multirow{3}{*}{20}   & 20       & \textbf{11404.8}  & \textbf{11404.8}  & \textbf{11404.8}  & \textbf{11404.8}  & \textbf{11404.8}           \\
		&&30   & \textbf{16770.2} & 16758.45 & 16715.19 & 16755.75 & 16570.96                   \\
		&&40   & \textbf{21977.17} & 21963.8 & 21643.56 & \textbf{21977.17} & 21874.04                     \\
		\hline
		\multirow{6}{*}{WR36} &  \multirow{3}{*}{10}    & 20       & 19022.77 & \textbf{19221.44} & \textbf{19221.44} & 19193.42 & \textbf{19221.44} \\
		&& 30   & 27247.5  & 27442.9  & 27418.74 & 27387.06 & \textbf{27450.99}                  \\
		&&40   & 34671.62 & \textbf{34938.65} & \textbf{34938.65} & 34817.27 & 34888.81                  \\
		\cline{2-8}
		&  \multirow{3}{*}{20}   & 20       & 18448.64 & 19336.33 & 19172.56 & 19354.23 & \textbf{19441.17}          \\
		&&30   & 26367.2  & 27752 & 27785 & 27492.11 & \textbf{27975.55}                     \\
		&&40   & 33451.94 & \textbf{35665.6}  & 35127.32 & 35065.85 & 35604.45  \\
		\bottomrule                   
	\end{tabular}

	\vspace{0.5em}
	\caption{Total Expected Power (kW/year) after 100 seconds as function of benchmark and method \todo{Change to 100 seconds and re-arrange our benchmarks first.} }\label{tab:results1}
\end{table}

@@

	\begin{tabular}{| c | c | c | c | c | c | c | c |}
		\toprule
		Wind Directions  & n        & m        & ILP-LS       & QP-LS       & QUBO-LS       & QP-SS       & DA-LS     \\
		\toprule
		\multirow{6}{*}{WR1}  & \multirow{3}{*}{10}       & 20       & \textbf{11185.41} & \textbf{11185.41} & \textbf{11185.41} & \textbf{11185.41} & \textbf{11185.41} \\
			& & 30   & 15739.57 & 15738.45 & \textbf{15742.93} & 15735.1  & 15740.69         \\
		& & 40 & \textbf{19265.21} & \textbf{19265.21} & 18952.97 & \textbf{19265.21} & \textbf{19265.21}                \\
				\cline{2-8}
		&\multirow{3}{*}{20}   & 20       & \textbf{11404.8}  & \textbf{11404.8}  & \textbf{11404.8}  & \textbf{11404.8}  & \textbf{11404.8}           \\
		&&30   & \textbf{16770.2} & 16758.45 & 16715.19 & 16755.75 & 16570.96                   \\
		&&40   & \textbf{21977.17} & 21963.8 & 21643.56 & \textbf{21977.17} & 21874.04                     \\
		\hline
		\multirow{6}{*}{WR36} &  \multirow{3}{*}{10}    & 20       & 19022.77 & \textbf{19221.44} & \textbf{19221.44} & 19193.42 & \textbf{19221.44} \\
		&& 30   & 27247.5  & 27442.9  & 27418.74 & 27387.06 & \textbf{27450.99}                  \\
		&&40   & 34671.62 & \textbf{34938.65} & \textbf{34938.65} & 34817.27 & 34888.81                  \\
		\cline{2-8}
		&  \multirow{3}{*}{20}   & 20       & 18448.64 & 19336.33 & 19172.56 & 19354.23 & \textbf{19441.17}          \\
		&&30   & 26367.2  & 27752 & 27785 & 27492.11 & \textbf{27975.55}                     \\
		&&40   & 33451.94 & \textbf{35665.6}  & 35127.32 & 35065.85 & 35604.45  \\
		\bottomrule                   
	\end{tabular}

\vspace{0.5em}
\caption{Total Expected Power (kW/year) after 3600 seconds as function of benchmark and method}\label{tab:results2}
\end{table}

>>>>

In this section, we 
present an empirical evaluation of the two quadratic models based on 
12 standard WFLO instances.
Our main results are: \begin{itemize}
	\item QUBO based WFLO using the digital annealer (DA) achieves a similar performance to state-of-the-art exact methods.
		\item The runtime for solving the QUBO model on the DA is two orders of magnitude lower than QCOP.  
	\item Given sufficient runtime, solving the QCOP model yields superior results on the larger instances.
\end{itemize}
We start by outlining the experimental design of our evaluation, followed by an overview of our main results,
and conclude the section with a discussion of the results together with the limitations of our approach.

@@

\paragraph{WFLO Instances and Energy Measurement}

To test and benchmark our models, we used 12 standard benchmark WFLO instances
from the literature~\cite{MOSETTI1994105,Zhang2014,grady2005placement}. 
The 12 benchmarks result from varying 2 wind settings (1 and 36 wind directions),
2 grid sizes ($10\times10$ with cell size $200$ meters and $20\times20$ with cell size $100$ meters),
and 3 variations for number of turbines ($m \in \{20, 30 or 40\}$).
The wind regime distribution presented in Figure~\ref{fig:prob_wind} was 
elicited from~\cite{Zhang2014}.
Additional parameters that were used to calculate 
the velocities ($u_{id\infty}, u_{ijd}$) include: turbine height ($60$ meters),
ground roughness ($0.3$ meters), turbine rotor radius ($20$ meters), and a wind farm of size $2km \times 2km$.
We have measured solutions using the SS energy expression.
To to this end, we converted solutions that came from LS based methods into the corresponding SS expression; 
the total mean energy is calculated in $kW/year$.

@@

We compared our two models, namely QCOP and QUBO, against two state of the art exact optimization methods:
the integer linear programming (ILP-LS) approach from~\cite{donovan2005wind}, and the 
model that uses a quadratic approximation (QP-SS)~\cite{turner2014new}. The CP approach presented in~\cite{Zhang2014} was
reported to perform worse than the rest and was left out of the experiments.
We used state of the art software, namely Gurobi~\cite{gurobi}, to solve QCOP, ILP-SS and QP-SS. 
We shall refer to the QCOP problem as QP-LS as it is a quadratic program that uses the LS objective.
In addition, we 
applied both Fujitsu's digital annealer and Gurobi to solve the QUBO variant of WFLO. We shall refer to the former as DA-LS, and to the latter
as QUBO-LS.

@@

For exact methods (QP-SS, ILP-LS, QP-lS and QUBO-LS),
we ran Gurobi with a time limit of 3600 seconds. We collected all feasible solutions
until that point in time. The best solution in terms of energy is the solution that attained the highest objective
values (SS in QP-SS and LS in the rest of the methods).
For the digital annealer, we used a single configuration that was found to work best across the different instances \todo{Jason, please insert details about the DA config. here} The DA ran until convergence of the underlying simulated annealing algorithm and the runtime 
of the procedure was recorded. \todo{@Chris: do we want to share the code that ran the experiments in batches? perhaps it should be separated from the problem construction and the two need to be shared separately}

The exact methods were all solved using Gurobi's quadratic programming solver on \todo{Jason, please add machine details here}. Furthermore, QUBO-LS was solved on DA version 1 \todo{Eldan: any additional info that we need to add here?}.

@@

	\begin{tabular}{| c | c | c | c | c | c | c | c |}
		\toprule
		Wind Directions  & n  & m  & DA-LS  & QUBO-LS  & QP-LS  & QP-SS  & ILP-LS  \\
		\toprule
		\multirow{6}{*}{WR1}  & \multirow{3}{*}{10}       & 20       & \textbf{11185.41} & \textbf{11185.41}* & \textbf{11185.41}* & \textbf{11185.41}* & \textbf{11185.41}* \\
		& & 30   & 15740.69 & \textbf{15742.93}  & 15738.45  & 15735.1  & 15739.57     \\
		& & 40 & \textbf{19265.21} & 18952.97 & \textbf{19265.21}  & \textbf{19265.21} & \textbf{19265.21}                \\
		\cline{2-8}
		&\multirow{3}{*}{20}   & 20       & \textbf{11404.8}  & \textbf{11404.8}*  & \textbf{11404.8}*  & \textbf{11404.8}*  & \textbf{11404.8}           \\
		&&30   & 16570.96 & 16715.19  & \textbf{16758.45}  & 16755.75 & 16695.05                  \\
		&&40   & 21874.04 & 21643.56  & 21905.5 & \textbf{21977.17} & \textbf{21977.17}        \\
		\hline
		\multirow{6}{*}{WR36} &  \multirow{3}{*}{10}    & 20       & \textbf{19221.44} & \textbf{19221.44} & \textbf{19221.44} & 19193.42 & 19022.77 \\
		&& 30  & \textbf{27450.99} & 27418.74 & 27442.9 & 27387.06 & 27247.5                     \\
		&&40   & 34888.81 & \textbf{34938.65} & \textbf{34938.65} & 34817.27  & 34671.62          \\
		\cline{2-8}
		&  \multirow{3}{*}{20}   & 20   & \textbf{19441.17}  & 19172.56 & 19336.33 & 19354.23  & 18448.64            \\
		&&30   & \textbf{27975.55} & 27443.8  & 27752 & 27492.11  & 26367.2                      \\
		&&40   & 35604.45 & 35127.32 & \textbf{35665.6}   & 35065.85 & 33451.94 \\
		\bottomrule                   
	\end{tabular}

	\vspace{0.5em}
	\caption{Total Expected Power (kW/year) after 100 seconds as function of benchmark and method. * stands for optimal solution. \todo{@Jason: could you please check if my marking of * for optimal solutions is correct? I think that optimality was proven only for $m=20$ and single wind direction, right?} }\label{tab:results1}
\end{table}

@@

	\begin{tabular}{| c | c | c | c | c | c | c | c |}
		\toprule
		Wind Directions  & n  & m  & DA-LS  & QUBO-LS  & QP-LS  & QP-SS  & ILP-LS  \\
		\toprule
		\multirow{6}{*}{WR1}  & \multirow{3}{*}{10}       & 20       & \textbf{11185.41} & \textbf{11185.41}* & \textbf{11185.41}* & \textbf{11185.41}* & \textbf{11185.41}* \\
		& & 30   & 15740.69 & \textbf{15742.93}  & 15738.45  & 15735.1  & 15739.57     \\
		& & 40 & \textbf{19265.21} & 18952.97 & \textbf{19265.21}  & \textbf{19265.21} & \textbf{19265.21}                \\
		\cline{2-8}
		&\multirow{3}{*}{20}   & 20       & \textbf{11404.8}  & \textbf{11404.8}*  & \textbf{11404.8}*  & \textbf{11404.8}*  & \textbf{11404.8} *          \\
		&&30   & 16570.96 & 16742.66  & 16758.45  & 16755.75 & \textbf{16770.2 }                 \\
		&&40   & 21874.04 & 21832.5  & 21963.81 & \textbf{21977.17} & \textbf{21977.17}        \\
		\hline
		\multirow{6}{*}{WR36} &  \multirow{3}{*}{10}    & 20       & \textbf{19221.44} & \textbf{19221.44} & \textbf{19221.44} & 19193.42 & 19213.96 \\
		&& 30  & \textbf{27450.99} & 27442.9 & 27442.9 & 27387.06 & 27389.21                     \\
		&&40   & 34888.81 & \textbf{34938.65} & \textbf{34938.65} & 34817.27  & 34856.45          \\
		\cline{2-8}
		&  \multirow{3}{*}{20}   & 20   & \textbf{19441.17}  & 19394.58 & 19336.33 & 19354.23  & 19368.86            \\
		&&30   & \textbf{27975.55} & 27785.74  & 27752 & 27492.11  & 27633.2                      \\
		&&40   & 35604.45 & 35480.9 & \textbf{35665.6}   & 35065.85 & 35210.78 \\
		\bottomrule                   
	\end{tabular}

\vspace{0.5em}
\caption{Total Expected Power (kW/year) after 3600 seconds as function of benchmark and method. * stands for optimal solution.}\label{tab:results2}
\end{table}
